### 2024-02-09 ms.qmd
Updates

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
### Red
mod_dar <- readRDS(here("output/models/deli_red.rds"))
resid_dar <- residuals(mod_dar)
### Blue
mod_dab <- readRDS(here("output/models/deli_blue.rds"))
resid_dab <- residuals(mod_dab)
## L. guichenoti
### Red
mod_gar <- readRDS(here("output/models/guich_red.rds"))
resid_gar <- residuals(mod_gar)
### Blue
mod_gab <- readRDS(here("output/models/guich_blue.rds"))
resid_gab <- residuals(mod_gab)
```

>>>>

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
### Red
mod_dar <- readRDS("./output/models/deli_red.rds")
resid_dar <- residuals(mod_dar)
### Blue
mod_dab <- readRDS("./output/models/deli_blue.rds")
resid_dab <- residuals(mod_dab)
## L. guichenoti
### Red
mod_gar <- readRDS("./output/models/guich_red.rds")
resid_gar <- residuals(mod_gar)
### Blue
mod_gab <- readRDS("./output/models/guich_blue.rds")
resid_gab <- residuals(mod_gab)
```
